### 2009-12-01 docs/marcello-dissertation/thesis/chapter10-appendix.tex
Updates to the images of the experiments and revisions to different chapters from 4 to 10.
git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@664 559edde2-a4d4-44e0-96fc-4035e40d7396

NetBEAMS uses the concept of the modularization through the use of the the
Producer-Consumer paradigm described in the previous section. Since the DSP
Components are essentially osgi-intro bundles, the interoperability between them are
given in the implementation and reuse existing bundles in the osgi-intro Framework
and the DSP Platform, described by an artifact called MANIFEST.MF as seen in
listing \cite{file:osgi-intro-manifest}. In general, an osgi-intro bundle must
provide specifications that describes the module to be published into the osgi-intro
Framework. In this way, the main properties of the osgi-intro MANIFEST.MF artifact can
used by the DSP Data Persistence can be summarized as follows:

\begin{itemize}
  \item \textbf{Bundle-Activator}: The name of the instance of an osgi-intro Activator
  class, responsible to manage the bundle. The implemented class
  ``DataPersistenceActivator'' provides the activation mechanisms for the
  services provided by the DSP Data Persistence Component;
  \item \textbf{Bundle-ClassPath}: the necessary Java Jars list needed to run
  the bundle. It lists the mongoDB Java driver as one of the required
  dependencies deployed in the same package;
  \item \textbf{Import-Package}: the Java Packages needed by the DSP Data
  Persistence Component Bundle. These Java Packages must be provided by other
  DSP components, forcing the execution to be dependent on those package.
  They are provided through a ``Export-Package'' section in other osgi-intro
  bundles and, as it is shown in listing \ref{file:osgi-intro-manifest}, they
  are from different packages.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{config.xml}: the DSP Data Persistence is added to the DSP
  Platform adding an entry for the component;
  \item \textbf{matcher\underline{ }config.xml}: the addition of the rules that
  filters the messages to the DSP Data Persistence;
  \item \textbf{DSPDataPersistence\underline{ }001.xml}: depicts the bootstrap
  message for the DSP Data Persistence Component, as shown in Listing 
  \ref{file:dsp-data-pers-bootstrap.xml}.
\end{itemize}

@@

Futon4Mongo is an open-source software adapted from CouchDB \ref{couchdb}.
First, the collections list is shown. Figure
\ref{fig:view-collections-instance-browser-futondb} shows one single collection
for the YSI data containing 1 million objects.

@@

\lstinputlisting[label=file:osgi-manifest,caption=OSGi Manifest
Descriptor]{../../../../netbeams/versions/v2/apps/osgi-bundles/dsp/DSPDataPersistence/META-INF/MANIFEST.MF}

@@

\lstinputlisting[language=Bash,label=file:experiment-setup-executor,caption=Experiment
Implementation]{../../../../netbeams/versions/v2/persistence/run-persistence-experiment}

\lstinputlisting[language=Java,label=file:random-ysi-data-generator,caption=Experiment
Implementation]{../../../../netbeams/versions/v2/apps/osgi-bundles/dsp/DSPSondeProducer/src/org/netbeams/dsp/ysi/SondeTestData.java}

\lstinputlisting[language=Java,label=file:experiment-dsp-implementation,caption=Experiment
Implementation]{../../../../netbeams/versions/v2/apps/osgi-bundles/dsp/DSPDataPersistence/src/org/netbeams/dsp/persistence/controller/DSPMessageToMongoDBExperiment.java}

@@

>>>>

NetBEAMS uses the concept of the modularization through the use of the the
Producer-Consumer paradigm described in the previous section. Since the DSP
Components are essentially osgi-intro bundles, the interoperability between them are
given in the implementation and reuse existing bundles in the osgi-intro Framework
and the DSP Platform, described by an artifact called MANIFEST.MF as seen in
Listing \ref{file:osgi-intro-manifest}. In general, an osgi-intro bundle must
provide specifications that describes the module to be published into the osgi-intro
Framework. In this way, the main properties of the osgi-intro MANIFEST.MF artifact can
used by the DSP Data Persistence can be summarized as follows:

\begin{itemize}
  \item \textbf{Bundle-Activator}: The name of the instance of an osgi-intro Activator
  class, responsible to manage the bundle. The implemented class
  ``DataPersistenceActivator'' provides the activation mechanisms for the
  services provided by the DSP Data Persistence Component;
  \item \textbf{Bundle-ClassPath}: the necessary Java Jars list needed to run
  the bundle. It lists the mongoDB Java driver as one of the required
  dependencies deployed in the same package;
  \item \textbf{Import-Package}: the Java Packages needed by the DSP Data
  Persistence Component Bundle. These Java Packages must be provided by other
  DSP components, forcing the execution to be dependent on those package.
  They are provided through a ``Export-Package'' section in other osgi-intro
  bundles and, as it is shown in Listing \ref{file:osgi-intro-manifest}, they
  are from different packages.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{config.xml}: the DSP Data Persistence is added to the DSP
  Platform adding an entry for the component;
  \item \textbf{matcher\underline{ }config.xml}: the addition of the rules that
  filters the messages to the DSP Data Persistence;
  \item \textbf{DSPDataPersistence\underline{ }001.xml}: depicts the bootstrap
  message for the DSP Data Persistence Component, as shown in Listing 
  \ref{file:dsp-data-persistence-bootstrap.xml}.
\end{itemize}

@@

Futon4Mongo is an open-source software adapted from CouchDB \cite{couchdb}.
First, the collections list is shown. Figure
\ref{fig:view-collections-instance-browser-futondb} shows one single collection
for the YSI data containing 1 million objects.

@@

\lstinputlisting[label=file:osgi-intro-manifest,caption=OSGi Manifest
Descriptor]{../../../../netbeams/versions/v2/apps/osgi-bundles/dsp/DSPDataPersistence/META-INF/MANIFEST.MF}

@@

\lstinputlisting[language=Bash,label=file:experiment-setup-executor,caption=Experiment
Main Execution Script]{../../../../netbeams/versions/v2/persistence/run-persistence-experiment}

\lstinputlisting[language=Bash,label=file:experiment-query-scenarios,caption=Experiment
Scenarios Implementation]{../../../../netbeams/versions/v2/persistence/experiment-client-scenarios.js}

\lstinputlisting[language=Java,label=file:random-ysi-data-generator,caption=Random
Test Data Generator]{../../../../netbeams/versions/v2/apps/osgi-bundles/dsp/DSPSondeProducer/src/org/netbeams/dsp/ysi/SondeTestData.java}

\lstinputlisting[language=Java,label=file:experiment-dsp-implementation,caption=Inserting
Random Data to MongoDB]{../../../../netbeams/versions/v2/apps/osgi-bundles/dsp/DSPDataPersistence/src/org/netbeams/dsp/persistence/controller/DSPMessageToMongoDBExperiment.java}

@@

\lstset{label=file:mongodb-export-command,caption=Export Command to CSV format}
\begin{lstlisting}
mongoexport -d netbeams -c SondeDataContainer --dbpath data --csv -f "_id,sensor_ip_address,transaction_time,fact_time,data.temperature,data.sp_condition,data.condition,data.resistence,data.salinitude,data.pressure,data.depth,data.ph,data.pH_mv,data.odo_sat,data.odo_condition,data.turbidity,data.battery" -o logs/experiment-483840-data-exported-20091129-190207.csv

Sun Nov 29 19:07:04 query netbeams.SondeDataContainer ntoreturn:0 reslen:2258 nscanned:101 { query: {}, $snapshot: 1 }  nreturned:101 202ms
Sun Nov 29 19:07:04 getmore netbeams.SondeDataContainer cid:7749363894863150628 ntoreturn:0 query: { query: {}, $snapshot: 1 }  bytes:1048562 nreturned:47661 1767ms
...
...
...
Sun Nov 29 19:10:18 getmore netbeams.SondeDataContainer cid:7749363894863150628 ntoreturn:0 query: { query: {}, $snapshot: 1 }  bytes:793098 nreturned:36049 1975ms
exported 2419200 records
\end{lstlisting}

### 2009-12-01 docs/marcello-dissertation/thesis/chapter4-netbeams-in-depth-requirements-analysis-and-specification.tex
Updates to the images of the experiments and revisions to different chapters from 4 to 10.
git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@664 559edde2-a4d4-44e0-96fc-4035e40d7396

As described in section \ref{sec:sn-infrastructure}, sensor devices produce
its observed data based on properties of measurements defined by its
manufacturer. SF-BEAMS can be seen a single-hop star sensor network containing
different instances of sensors, including the ``YSI 6600 ESD V2", as seen in
figure \ref{fig:ysi-device}, which is a powerful water quality monitoring
device that produces around 52 bytes (13x4 Bytes) on a single real-time data
stream as shown on table \ref{tab:ysi-data-stream}.

>>>>

As described in section \ref{sec:sn-infrastructure}, sensor devices produce
its observed data based on properties of measurements defined by its
manufacturer. SF-BEAMS can be seen a single-hop star sensor network containing
different instances of sensors. One example of such sensors is the ``YSI 6600
ESD V2", as seen in Figure \ref{fig:ysi-device}. Therefore, it can be seen as
a powerful water quality monitoring device that produces around 52 bytes (13x4
Bytes) on a single real-time data stream as shown on table
\ref{tab:ysi-data-stream}.
